\thetitle

### 2010-02-01 doc/paper.tex
doc: Fix university name and credit BRICKS/FOCUS project.
Ignore-this: 5627502dd551b7c29e383bd26bb96246

darcs-hash:20100201111628-bab43-f2099273d43230bcaee67fe50c8af341708d75b8.gz

\author{}
\institute{Institute for Computing and Information Sciences\\ Nijmegen University}

@@

\begin{abstract}
This technical report documents our development of a hybrid system safety prover, implemented in Coq using the abstraction method introduced by Alur in \cite{alur}. The development includes: a formalization of the structure of hybrid systems; a systematic approach and generic set of support utilities for the construction of an abstract system (consisting of decidable ``overestimators'' of abstract transitions and initiality) faithfully representing a (concrete) hybrid system; a translation of abstract systems to graphs enabling decision of abstract state reachability using a certified graph reachability algorithm; a proof of an example hybrid system (taken from \cite{alur}) generated using this tool stack. The development critically relies on the computable real number implementation part of the C-CoRN library of formalized constructive mathematics. \todo{Hm, anything else worth mentioning?}

>>>>

\author{\eelis}
\institute{Institute for Computing and Information Sciences\\ Raboud University Nijmegen}

@@

\begin{abstract}
This technical report documents our development of a hybrid system safety prover, implemented in Coq using the abstraction method introduced by Alur in \cite{alur}. The development includes: a formalization of the structure of hybrid systems; a systematic approach and generic set of support utilities for the construction of an abstract system (consisting of decidable ``overestimators'' of abstract transitions and initiality) faithfully representing a (concrete) hybrid system; a translation of abstract systems to graphs enabling decision of abstract state reachability using a certified graph reachability algorithm; a proof of an example hybrid system (taken from \cite{alur}) generated using this tool stack. The development critically relies on the computable real number implementation part of the C-CoRN library of formalized constructive mathematics. \todo{Hm, anything else worth mentioning?}\footnote{This research was supported by the BRICKS/FOCUS project 642.000.501 ``Advancing the Real use of Proof Assistants''.}
